---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rrrem

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

rrrem is an **R** port of the [**R**iver**R**EM](https://github.com/klarrieu/RiverREM) package, letting you use packages in R's spatial programming ecosystem to produce relative elevation models. Specifically, this package implements the river-retrieving and REM-producing elements of RiverREM; because R has such strong graphing support for raster graphics, the visualizations are not re-implemented (but are easily re-created using either base R or ggplot2). 

Please note that this package was made _extremely_ quickly and is effectively untested -- there may be some sharp edges yet to be sanded down, and 

## Installation

You can install the development version of rrrem like so:

``` r
remotes::install_github("mikemahoney218/rrrem")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rrrem)

dem <- sf::st_as_sf(
  data.frame(
    y = c(43.412402, 43.489347), 
    x = c(-123.591623, -123.479736)
  ),
  coords = c("x", "y"),
  crs = 4326
) |> 
  sf::st_transform(3857) |> 
  terrainr::get_tiles() |> 
  purrr::chuck("elevation") |> 
  terrainr::merge_rasters()

rem <- make_rem(dem)

terra::plot(rem)
```

```{r}
dem <- terra::rast(dem)

hillshade <- terra::shade(
  terra::terrain(dem, "slope", unit = "radians"),
  terra::terrain(dem, "aspect", unit = "radians")
)

trimmed_rem <- rem
trimmed_rem[trimmed_rem > 200] <- 200

par(mar = c(0, 0, 0, 0))
terra::plot(
  hillshade, 
  col = grey(0:100/100), 
  legend = FALSE, 
  axes = FALSE,
  xaxs="i", 
  yaxs="i"
)

terra::plot(
  trimmed_rem,
  col = viridis::mako(50, direction = -1), 
  legend = FALSE, 
  axes = FALSE,
  add = TRUE,
  alpha = 0.75,
  xaxs="i", 
  yaxs="i"
)
```



